Iterative construction of replicated designs based on Sobol' sequences

### 2016-06-14 crass/crassnew.tex
Small typos

At step $\ell \geq 1$, using formula (\ref{group.operation}) we construct:
\begin{equation}
B_\ell=\{\vx_i^{(0)}\oplus\ve_\ell\}_{i=0}^{2^r-1}, \qquad {B'}_\ell=\{{\vx'}_i^{(0)}\oplus{\ve'}_\ell\}_{i=0}^{2^r-1}.
\label{dig.shift}
\end{equation}
where $\ve_\ell \in \left(\mathbb{F}_2^{r}\right)^{s} \setminus \mathcal{P}_{\ell-1}$ and ${\ve'}_\ell \in \left(\mathbb{F}_2^{r}\right)^{s} \setminus \mathcal{P'}_{\ell-1}$. Indeed, $B_0$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$. Therefore, we construct $B_\ell=B_0 \oplus \ve_\ell$ as a coset of $B_0$ under the right choice of $\ve_\ell$. The same reasoning applies to ${B'}_0$.  Additions by vectors $\ve_j$ and ${\ve'}_j$ in (\ref{dig.shift}) are referred as digital shifts.

>>>>

At step $\ell \geq 1$, using definition \eqref{group.operation} we construct:
\begin{equation}
B_\ell=\{\vx_i^{(0)}\oplus\ve_\ell\}_{i=0}^{2^r-1}, \qquad {B'}_\ell=\{{\vx'}_i^{(0)}\oplus{\ve'}_\ell\}_{i=0}^{2^r-1}.
\label{dig.shift}
\end{equation}
where $\ve_\ell \in \left(\mathbb{F}_2^{r}\right)^{s} \setminus \mathcal{P}_{\ell-1}$ and ${\ve'}_\ell \in \left(\mathbb{F}_2^{r}\right)^{s} \setminus \mathcal{P'}_{\ell-1}$. Indeed, $B_0$ is a subgroup of $\left(\mathbb{F}_2^{r}\right)^{s}$. Therefore, we construct $B_\ell=B_0 \oplus \ve_\ell$ as a coset of $B_0$ under the right choice of $\ve_\ell$. The same reasoning applies to ${B'}_0$.  Additions by vectors $\ve_j$ and ${\ve'}_j$ in \eqref{dig.shift} are referred as digital shifts.
